\documentclass{article}
\usepackage{../tex/mysty}
\geometry{left=1.5in}
\usepackage[final]{pdfpages}
\begin{document}


\maketitlepage{U.S. Food and Drug Administration: Regulatory
  Report}{Sanjay Challa}

\setcounter{tocdepth}{3}
\tableofcontents
\newpage

\section*{Executive summary}
\label{sec:exec-summary}
This focus of this document is on relevant FDA regulation of the
device our team has designed. The first section of this document
provides a general overview of FDA regulation of medical devices. The
FDA regulatory overview covers device classes, filing requirements for
510(k) and IDE/PMAs, and the meanings of FDA \textit{clearance} and
FDA \textit{approval}. The second section of this document covers FDA
regulation specific to our device. In this document, we explain that
the FDA currently does not regulate our device. We further outline
that since our device is meant only for use in research settings, does
not come into contact with patients, and is not used for diagnosis or
treatment, our device should not be regulated by the FDA. Our device
is simply a laboratory device intended for measurement purposes. While
there are a few standards from the FD \& C act which may apply to our
device, the primary performance standard of our device derives
directly from our client's needs and our design specifications. The
appendix of this document contain a mock Traditional 510(k) for our
device. In preparing the Traditional 510(k), we assumed that our
device was regulated as a Class II device by the FDA, and did our best
to draft the 510(k) under this premise. There are a number of elements
of the 510(k) which were trivial in relation to our device as our
device is not currently regulated by the FDA. 

\section{Regulation Overview}
\label{sec:test-administration}

Medical devices are classified into Class I, II, and III based on the
level of regulatory control required by the FDA. All devices must
comply with the Class I General Controls. These include annual
establishment registration, or registration of owners and operators of
facilities that are involved in the production and distribution of
medical devices, as well as a medical device listing of all products
produced at a certain establishment. Devices must be made in
accordance with current good manufacturing practices (cGMPs), and
manufacturers must develop a system of quality control that in line
with any FDA quality systems (QS) guidelines applicable to their
device. All manufacturing processes and procedures must be
documented. The labeling on the device, including the claims and
advertising, should be in accordance with FDA regulations; it should
be clear, should not be misleading, and should not omit any required
important warnings. Finally, as required by FDA Medical Device
Reporting regulations, medical device manufacturers must report to the
FDA any complaints of malfunction of medical devices as well as
serious injuries or deaths associated with medical devices.

Class II products are defined as products for which general controls
alone are insufficient to assure safety and effectiveness.” Orthopedic
and craniofacial implants are Class II products, as opposed to manual
wheelchairs and hand-held surgical instruments, which are Class I
products.  In addition to following Class I General Controls, Class II
products are subject to Standards or Guidance Documents such as ASTM
or ISO Standards or OCD and OCER Guidance.

For Class II products, manufacturers or companies must submit a
premarket notification in the form of a 510(k). A 510(k) submission
requires the device name, the establishment registration number, the
device classification, documentation of performance standards, and
proposed labels and advertisements, as described in Class I General
Controls. In addition, a 510(k) submission requires a description of
“predicate devices” – devices already in the market that are similar
to the proposed product – and a statement detailing the similarities
and differences between predicate devices and the proposed
device. 510(k) clearance is based on substantial equivalency, which
means that “the new device is at least as safe and effective as the
predicate.” Predicate devices may be in any of the three device
classes. A product is substantially equivalent if it has the same
intended use and technological characteristics as the predicate
device. If a device has the same intended use as the predicate but
different technological characteristics, it should be proven to be as
safe and effective as the predicate and should not raise any new
safety issues.

Class III products are defined as those which “support or sustain
human life, are of substantial importance in preventing impairment of
human health, or which present a potential, unreasonable risk of
illness or injury.” A Pre-Market Approval (PMA) submission and, in
some cases, an investigational device exemption (IDE) are required for
approval of Class III devices. (An IDE may also be required for some
Class II product clearances). An IDE allows the investigational device
to be used in a clinical study, approved both by the FDA and an
Institutional Review Board, to collect safety and effectiveness data
required for a PMA.  In contrast to Class II devices, Class III
devices must receive FDA approval instead of clearance for their use,
components, and manufacturing methods. Class III devices are
significantly different from devices already existent on the market
and present new safety concerns that have not been tested. PMAs must
not only comply with Class I General Controls, but must also
demonstrate the safety and effectiveness of the device and include
both good science and scientific writing.
	 

\section{Device Classification}
\label{sec:protocols}

Searches in the \textit{FDA Product Classification Database} using the
keywords ``tomography,'' ``ophthalmic,'' and ``micrometer'' were
performed. A few entrys were returned which related to our device:

\begin{enumerate}
\item Optical coherence tomography: General \& Plastic Surgery panel,
  regulation number 886.1570, product code OBO; describes an
  ophthalmoscope as an "Diagnostic device to aid in the detection and
  management of various ocular diseases" capable of "viewing, imaging,
  measurement, and analysis of ocular structures."
\item System, x-ray, tomography, computed: Radiology panel, regulation
  number 892.1750, product code JAK; describes a diagnostic x-ray
  system which relies upon similar technical principles as our
  device. The similarity lies in the method by which measurement
  slices are taken, and the manner in which measurement slices are
  combined to create a reconstruction.
\item Micrometers, Microscope: Pathology panel, regulation number
  864.3600, product code KEH; describes a microscopes and accessories
  as optical instruments used to enlarge images of specimens,
  preparations, and cultures for medical purposes.
\end{enumerate}

While the devices listed above share some common elements with our
device, none of the devices fully capture the intended use and
functionality of our device. One key difference between our device and
those listed above is that our device is not intended for any
diagnotic or clinical applications, but is instead targeted at
research applications. In this regard, our device is most likely not
regulated by the FDA as medical device. According to the FD\&C Act
21USC321, a "device" is "an instrument, apparatus, implement, machine,
contrivance, implant, in vitro reagent, or other similar or related
article, including any component, part, or accessory, which is:

\begin{itemize}
\item recognized in the official National Formulary, or the United
  States Pharmacopeia, or any supplement to them,
\item intended for use in the diagnosis of disease or other
  conditions, or in the cure, mitigation, treatment, or prevention of
  disease, in man or other animals, or
\item intended to affect the structure or any function of the body of
  man or other animals, and which does not achieve its primary
  intended purposes through chemical action within or on the body of
  man or other animals and which is not dependent upon being
  metabolized for the achievement of its primary intended purposes."
\end{itemize}

Our device clearly does not fall within any of the elements of the
above definition. It is not listed in the National Formulary, US
Pharmacopeia, nor any supplements to them. Furthermore, our device is
not intended for the diagnosis of disease or other conditions, or in
the cure, mitigation, treatment, or prevention of disease, in man or
other animals. It is solely intended for the measurement of eyeballs
dissected out of mice in research settings. Lastly, our device is not
inteneded for and does not affect the structure or functionality of
any man or animal. 

To conclude, an item by item search in Title 21 of the Code of Federal
Regulations (CFR), part 886 (ophthalmic panel), part 864 (pathology
panel), and part 892 (radiological panel) confirms that our device is
not substantially equivalent to any of the existing devices. While our
device has similar technological and/or functional characteristics, it
differs significantly, as described above. However, considering the
presence of electronic and visible radiation emitting components in
our device, regulations in the FD\&C Act sections 531-542 Electronic
Product Radiation Control provisions are still applicable to our
device. We believe that our device does not need to be directly
regulated by the FDA as it is meant for use solely in reserach
settings, does not come in contact either directly or indirectly with
patients, and is not used for diagnosis or treatment. 

\appendix

\refstepcounter{section}
\addcontentsline{toc}{section}{\thesection
  \hspace{1em}510(k) Premarket Notification}
% Cover sheets
\input{pages/cdrh-cover}
\input{pages/cover}
\input{pages/indications}
\input{pages/statement}
\input{pages/truthbomb}
\input{pages/certification} % Certified SE to Class I instead of CIII
\input{pages/financial}
\input{pages/conformity}

% Real sections
\newpage
\setcounter{subsection}{0}
\subsection{Executive Summary}

\newpage
\subsection{Device Description}

The described device (eyeScan Mezzo) is a bench-sized digitizer able
to accurately measure the three-dimensional surface structure of small
organic forms. Specifically designed to measure the convex shape of
dissected rat eyes down to \SI{2}{\micro m} resolution its likely
usage would involve research aims with respect to eye shape,
morphology, or development especially using genetically modified mouse
models.

In order to achieve these requirements the device must utilize an LED
micrometer, two motor/encoder acutator systems, and a system
controller. The device must be able to accurately position the
micrometer and the loaded object to the \SI{2}{\micro m} level.

Additionally, the device uses a sophisticated loading harness to hold
and rotate the object without needing to account for object
deformation under stress. This harness involves a number of opticaly
clear pieces and a methyl cellulose support polymer.

\newpage
\subsection{Substantial Equivalence Discussion}

\newcolumntype{Y}{>{\raggedright\arraybackslash}X}
\begin{figure}[H]
  \begin{tabularx}{\textwidth}{YYYY}
    \toprule
    Characteristcs & \mbox{Microscopes} and \mbox{Micrometers} & Optical Coherence \mbox{Tomography} & Computed X-ray \mbox{Tomography} \\ 
    \hline
    Intended Use & x & x &  \\
    \\
    Measurement Approach &   &  & x \\ 
    \\
    Anatomical Site of Interest & & x &  \\
    \\
    Output & & & x \\
    \bottomrule
  \end{tabularx}
  \caption{\textbf{Table of Substantially Equivalent Comparisons:}
    This table compares our device against substantially equivalent
    devices.}
\end{figure}

\subsubsection{Comparison to Microscopes and Accessories}
Microscopes and accessories are described by the FDA (regulation
number: 864.3600; product code: KEH) as optical instruments used to
enlarge images of specimens, preparations, and cultures for medical
purposes. Our device is similar in the sense that it is an optical
instrument, as it relies on a LED laser to take
measurements. Furthermore, our device is similar in that the sample to
be measured, namely mouse eyeballs, can be classified as a type of
``tissue specimen.''

Our device differs from microscopes in a number of ways. While the
measurement is optical, the method in which the sample is measured is
very different -- unlike microscopes, our devices takes
cross-sectional measurement slices by rotating the sample between the
LED micrometer. Our device also differs in that it further processes
the stack of cross-sectional measurements to generate a
three-dimensional reconstruction of the sample. Our device is also
specfically intended to be used with mouse eyeballs. Lastly, our
device is intended for use only in research settings, wheras
microscopes are allowed for use in medical settings.

\subsubsection{Comparison to Optical Coherence Tomography}
Ophthalmoscopes are described by the FDA (regulation number: 886.1570;
product code: OBO) as diagnostic devcies which aid in the detection
and management of various ocular diseases [\ldots] capable of viewing,
imaging, measurement, and analysis of ocular structures. Our device is
similar in that it precisely measures eyeballs and reconstructs their
three dimensional external surface. Our device is clearly focused on
the same anatomical site.

Our device differs from ophthalmoscopes in a number of ways. Unlike
ophthalmoscopes, our device makes measurements using an LED
laser. Furthermore, our device differs in that it also takes
cross-sectional slices by rotating the sample between the LED
micrometer. Additionally, our device differs in that its intended use
is not at all diagnostic in nature. 

\subsubsection{Comparison to X-Ray Computed Tomography}
Our device is similar to x-ray computed tomography systems in that it
makes similar cross-sectional measurements of samples. Our device is
also similar in that invovles a similar back-projection based
reconstruction in generating the three dimensional surface of the
measured object. 

Our device is different from x-ray computed tomography systems in that
it uses a laser which emits in the visible spectrum as opposed to
x-ray radiation. Our device is also different in that it is not
inteded for medical use, nor for use with live subjects. Our device is
instead intended for use with dissected mouse eyeballs in research
settings.

\newpage
\input{pages/labels}
\newpage
\input{pages/sterile}
\newpage
\input{pages/biocompatible}
\newpage
\subsection{Software}

The software elements in the described device are considered to be of
\textit{minor regulatory concern} since neither the device nor the
output of its software can in any way, direct or indirect, cause harm
to operators or patients or deliver information useful in a medical
diagnosis. The software involved with this device includes control and
automation firmware for the motion of the device's frame, recording
and reconstruction algorithms for interpreting data from the
micrometer, and standalone software on a general purpose computer for
control and viewing of the reconstructed meshes.

The device is non-hazardous in that neither the operator nor the
patient have any contact, direct or indirect, with the device while it
is operational.

The software requirements involve three stages: automation,
reconstruction, and control. 

\begin{itemize}
\item The \textit{automation} section is required to accurately
  control position of the measured piece and the micrometer within the
  device while maintaining accurate realtime position information from
  the motor encoders. This section will be written in National
  Instrument's (NI) LabView Realtime and compiled to very-high-speed
  integrated circuit hardware description language (VHDL) and deployed
  on an NI Reprogrammable Input Output (RIO) device.
\item The \textit{reconstruction} section is required to produce
  online reconstructions of the measured data in a format readable
  offline. This is instrumental in troubleshooting the usage of the
  device during the scan and must also be carefully implemented to
  prevent distortions. This section will be programmed partly in
  LabView Realtime for any realtime processing as to be deployed on
  the RIO and then completed in compiled C on the general purpose
  platform.
\item The \textit{control} section is the standalone software deployed
  on a general purpose computer and in communication with the
  device. This software both allows realtime feedback to the operator
  from the device and also allows for sequence programming and
  control. This section will be programmed in Python and deployed on
  the general purpose computer platform.
\end{itemize}

The funtional software testing and validation are largely functional
and have been previously specified in the previous Testing and
Verification Protocol document. Current testing status has not yet
reached the software level and therefore no results yet exist. The
Testing and Verification Protocol document is available at request.
\newpage
\input{pages/elec}

%\subsection{Performance Testing --- Lab, Animal, Clinical}
% Not required


\newpage
\addcontentsline{toc}{section}{References}
\bibliographystyle{unsrt}
\bibliography{../tex/bibl}

\end{document}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
