\newpage
\addcontentsline{toc}{subsection}{510(k) Cover Letter}
\singlespacing

\begin{flushright}
  \huge{510(k) Submission --- Traditional}\\[.5in]
  
  \begin{minipage}{0.8\textwidth}
    \begin{flushright}
      \large \textbf{Scanner: eyeScan Mezzo} \\
      \textit{\today}
    \end{flushright}
  \end{minipage}
\end{flushright}

\begin{flushleft}
  Joseph Abrahamson\\
  $<$\textit{abrahamson.j@gatech.edu}$>$ \\
  Phone: 770 601 4606 \\[1em]
  
  \textit{Will register establishment following FDA clearance.}
\end{flushleft}
\vspace{4em}

\onehalfspacing

We seek FDA clearance to market our device, \textbf{eyeScan Mezzo}, a
Class II medical device used for medical scanning of three-dimensional
exterior eye shape. To our knowledge FDA has not classified this
device and, thus, no product code has been assigned or requested for
this device in the Classification Database. Substantially equivalent
devices belong to the General \& Plastic Surgery, Radiology, and
Pathology panels. This finished component is a novel device not
previously marketed with FDA clearance in the USA. We require 510(k)
clearance due to substantial equivalence with existent optical
coherence tomography devices (regulation no. \textbf{886.1570},
product code \textbf{OBO}), x-ray computed tomography devices
(regulation no. \textbf{892.1750}, product code \textbf{JAK}), and
microscopes, micrometers, and accessories (regulation
no. \textbf{864.3600}, product code \textbf{KEH}). Manufacturing
registration is currently unspecified. 

With regards to performance standards, this device contains electrical
components, and is subject to testing under IEC 60601-1-2 Part
I. Furthermore, the device contains a laser component, which under 21
CFR 1000 dictates that the device falls under RCHSA controls. RCHSA
controls indicate that the manufacture of the laser component of this
device is subject to standards 1002.10, 1002.13, and 1002.30, which
specifiy necessary reporting on the manufacturing of the laser
component. Lastly, while the device does contain a laser, it is exempt
from 21 CFR 1040.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../reg"
%%% End:

